MCMC convergence diagnostics

### 2023-01-12 src/naomi-simple_mcmc/mcmc-convergence.Rmd
Small edits final

---
title: "MCMC convergence diagnostics`"
author:
- name: Adam Howes
output:
  bookdown::html_document2:
    toc: yes
    toc_float: yes
    toc_collapsed: yes
    df_print: paged
    code_folding: show
    theme: lumen
abstract: |
  **Background** In the report `naomi-simple_fit` with parameter `tmbstan = TRUE`, we used the NUTS algorithm to perform MCMC inference for the simplified Naomi model.

@@

area_merged %>%
  filter(area_level == max(area_level)) %>%
  print(n = Inf)

neighbours_pairs_plot("log_or_gamma", 5) #' Nkhata Bay and neighbours
neighbours_pairs_plot("log_or_gamma", 26) #' Blantyre and neighbours
```

>>>>

---
title: "MCMC convergence diagnostics"
author:
- name: Adam Howes
output:
  bookdown::html_document2:
    toc: yes
    toc_float: yes
    toc_collapsed: yes
    df_print: paged
    code_folding: show
    theme: lumen
abstract: |
  **Background** In the report `naomi-simple_fit` with parameter `tmbstan = TRUE`, we used the NUTS algorithm to perform MCMC inference for the simplified Naomi model.

@@

# area_merged %>%
#   filter(area_level == max(area_level)) %>%
#   print(n = Inf)
```

Here are Nkhata Bay and neighbours:

```{r}
neighbours_pairs_plot("log_or_gamma", 5) 
```

And here are Blantyre and neighbours:

```{r}
neighbours_pairs_plot("log_or_gamma", 26)
```
